\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.4cm]{geometry}
\usepackage{fontspec}
\IfFontExistsTF{Inter}{
    \setsansfont{Inter}
}{
    \setsansfont{Open Sans}
}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlist[itemize]{leftmargin=1em, itemsep=2pt, topsep=2pt}

\hypersetup{
    colorlinks=true,
    urlcolor=black,
    pdfborder={0 0 0}
}

\titleformat{\section}{\large\bfseries}{}{0pt}{}

\begin{document}

{\Huge Alin Nedelcu}

\faLinkedin{} \href{https://linkedin.com/in/asnedelcu}{linkedin.com/in/asnedelcu}  \\
\faGlobe{} \href{https://end.works}{end.works} \\
\faEnvelope{} \href{mailto:alin@end.works}{alin@end.works} \\
\faPhone{} +34 653 751 742 

\section*{Experience}

\textbf{Freelance — Remote} \hfill Nov 2024 -- Current \\
\textit{Full-Stack Developer} \\
Build and ship \textbf{iOS} and \textbf{Android} apps with secure storage, real-time features, analytics, and subscriptions. Also develop \textbf{websites for small local businesses} such as restaurants and shops, helping them present their products and services online. Lead \textbf{architecture}, \textbf{CI/CD}, \textbf{testing}, and full publishing workflows. Manage full product lifecycle from development to store release. \\
\textit{Tech:} \textbf{React Native}, \textbf{Expo}, \textbf{TypeScript}, \textbf{Redux Toolkit}, \textbf{Firebase}, RevenueCat, HealthKit/Health Connect, MMKV, Encrypted Storage, i18next

\textbf{Aimsun — Barcelona, Spain} \hfill Oct 2022 -- Nov 2024 \\
\textit{Software Engineer} \\
Built and maintained core modules for a \textbf{large SaaS platform}, including authentication, accounts, subscriptions, licensing, and MFA. Developed internal tools for \textbf{billing}, \textbf{permissions}, and user administration. Contributed to shared auth libraries and real-time data visualization interfaces. \\
\textit{Tech:} \textbf{React}, \textbf{Angular}, \textbf{TypeScript}, \textbf{Node.js}, Docker, GitLab CI/CD

\textbf{Viewnext — Madrid, Spain} \hfill Dec 2021 -- Oct 2022 \\
\textit{Software Developer} \\
Developed a \textbf{real-time monitoring dashboard} for a nationwide energy service, including route planning, maps, and booking flows. Improved API reliability, enhanced performance, and collaborated with QA to stabilize releases. \\
\textit{Tech:} Angular, TypeScript, Mapbox, Jenkins, REST APIs

\textbf{adidas — Zaragoza, Spain} \hfill May 2021 -- Dec 2021 \\
\textit{Software Developer} \\
Rebuilt legacy internal tools with modern web tech, delivering an improved \textbf{content editor}. Implemented \textbf{internationalization} and optimized translation workflows. Worked with design and content teams to streamline publishing in an Agile environment. \\
\textit{Tech:} Angular, TypeScript, Node.js, Jenkins, i18n

\textbf{Eleven Paths — Valencia, Spain} \hfill Dec 2019 -- May 2021 \\
\textit{Software Developer} \\
Migrated a governance and risk platform to a modern \textbf{Angular} architecture. Added enterprise features, improved UX, and maintained backend services for reporting and risk modeling. \\
\textit{Tech:} Angular, Java, Spring, PostgreSQL

\textbf{Ingenia Sistemas Avanzados para el Transporte — Zaragoza, Spain} \hfill Oct 2017 -- Dec 2019 \\
\textit{Software Developer} \\
Built a \textbf{responsive ticketing system} with online payments and admin tools, plus a mobile app with real-time arrivals and alerts. Collaborated with backend, design, and operations teams to improve reliability. \\
\textit{Tech:} Angular, Cordova, Node.js, MySQL, Nginx

\textbf{Rana Negra — Zaragoza, Spain} \hfill Mar 2017 -- Sep 2017 \\
\textit{Front-End Developer} \\
Built dynamic websites using a modular CMS and developed custom interactive components. Created an email automation tool with subscription billing. \\
\textit{Tech:} Symfony, Angular, Stripe, HTML/CSS

\section*{Leadership \& Volunteering}

\textbf{Founder — Asociación Cultural Brovrashgka} \hfill 2014 -- 2017 \\
Created and led a youth association focused on \textbf{anime and Japanese pop culture}. Organized multiple cultural events, workshops, and community activities with growing attendance. Managed \textbf{project planning}, \textbf{budgets}, \textbf{volunteers}, and event logistics. Coordinated teams, built partnerships, and delivered engaging activities for the local community.

\section*{Formation}

\textbf{Decree} — Development of \textbf{Multiplatform Applications} \\
\textit{CPIFP Los Enlaces} — Zaragoza \hfill 2014--2016

\textbf{Google Cloud Professional Cloud Architect} \\
\textit{Formación San Miguel} \hfill 2025

\textbf{Oxford Test of English — Advanced (C1)} \hfill 2023

\textbf{Languages:} Spanish, Romanian, English (C1)

\section*{Projects}

\textbf{Zierzo} — \href{https://zierzo.end.works}{zierzo.end.works} \\
City mobility and leisure app for Zaragoza with \textbf{real-time bus/tram schedules}, route info, and cinema listings. \\
\textit{Tech:} \textbf{React Native}, \textbf{Expo}, \textbf{Redux Toolkit}, MMKV, \textbf{Firebase}, RevenueCat, Google Mobile Ads, FlashList, Reanimated, Bottom Sheet, TypeScript, Nest.js, MongoDB

\textbf{LoveLust} — \href{https://lovelust.end.works}{lovelust.end.works} \\
Private \textbf{wellness and intimacy tracker} with a focus on privacy and customization. \\
\textit{Tech:} \textbf{React Native}, \textbf{Expo}, \textbf{TypeScript}, \textbf{Redux Toolkit}, \textbf{Firebase}, RevenueCat, HealthKit/Health Connect, MMKV, Encrypted Storage, i18next

\section*{Tech Stack}

\textbf{Front-end:} React 18/19, Angular 2--18, Next.js, React Native, Expo, Vite, Tailwind, Zustand, Redux Toolkit \\
\textbf{Back-end:} Node.js, Nest.js, Express, GraphQL, REST APIs \\
\textbf{Cloud / DevOps:} GCP (\textbf{Firebase}, Compute, Storage), Docker, Nginx, CI/CD (\textbf{GitLab}, \textbf{GitHub Actions}, Jenkins) \\
\textbf{Testing:} Jest, React Testing Library, Cypress, Karma \\
\textbf{Databases:} MongoDB, PostgreSQL, MySQL, Firebase Firestore/RealtimeDB \\
\textbf{Other:} TypeScript, Git, Mapbox, Webpack, Performance Optimization

\end{document}
