\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.6cm]{geometry}
\usepackage{fontspec}
\setmainfont{Inter}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}

\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlist[itemize]{leftmargin=1.1em, topsep=2pt, itemsep=2pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]

\begin{document}

{\Huge Alin Nedelcu}

\faPhone{} +34 653 751 742 \\
\faEnvelope{} \href{mailto:asnedelcu@icloud.com}{asnedelcu@icloud.com} \\
\faGlobe{} \href{https://end.works}{homepage} \\
\faLinkedin{} \href{https://linkedin.com/in/asnedelcu}{linkedin.com/in/asnedelcu}

\section*{Experience}

\textbf{Software Engineer} \hfill Oct 2022 -- Nov 2024 \\
Aimsun — Barcelona, Spain
\begin{itemize}
    \item Developed user panels for account, subscription, license, and 2FA management.
    \item Built admin interfaces for license assignment, billing editing, and project access control.
    \item Created a shared authentication module used across multiple apps.
    \item Contributed to front-end modules in Aimsun Live, a real-time traffic prediction platform.
\end{itemize}

\textbf{Software Developer} \hfill Dec 2021 -- Oct 2022 \\
Viewnext — Madrid, Spain
\begin{itemize}
    \item Built Iberdrola’s EV charging web app supporting 8,000+ real-time stations.
    \item Developed route planning tools and optimized booking workflows.
    \item Coordinated with backend and QA for stable API integrations.
\end{itemize}

\textbf{Software Developer} \hfill May 2021 -- Oct 2021 \\
adidas — Zaragoza, Spain
\begin{itemize}
    \item Refactored legacy content editor to a modern, unified stack.
    \item Implemented internationalization and locale management workflows.
    \item Worked in a cross-functional Scrum team improving content lifecycle.
\end{itemize}

\textbf{Software Developer} \hfill Dec 2019 -- Feb 2021 \\
Eleven Paths — Valencia, Spain
\begin{itemize}
    \item Migrated SandaS GRC from legacy JS/Java to Angular 2 with upgraded UI/UX.
    \item Maintained Java backend modules and expanded enterprise GRC features.
    \item Improved risk assessment tools, gap analysis, and reporting dashboards.
\end{itemize}

\textbf{Software Developer} \hfill Oct 2017 -- Dec 2019 \\
Ingenia Sistemas Avanzados para el Transporte — Zaragoza, Spain
\begin{itemize}
    \item Built a responsive ticketing platform with payment integrations.
    \item Developed admin tools for schedules, bus lines, drivers, and real-time data.
    \item Created a mobile app with bus arrival predictions and push notifications.
\end{itemize}

\textbf{Front-End Developer} \hfill Mar 2017 -- Aug 2017 \\
Rana Negra — Zaragoza, Spain
\begin{itemize}
    \item Built dynamic client websites using Symfony with modular CMS.
    \item Led development of an email management tool using Angular 2 and Stripe.
\end{itemize}

\section*{Formation}

\textbf{FP2} — Desarrollo de Aplicaciones Multiplataforma \\
CPIFP Los Enlaces, Zaragoza \hfill 2014–2016

Spanish, Romanian, English

\section*{Projects}

\textbf{LoveLust} — \href{https://lovelust.end.works}{lovelust.end.works} \\
Private wellness and intimacy tracker for mobile, designed for full privacy and customization.  
Tech: React Native, Expo, TypeScript, Redux Toolkit, Firebase, RevenueCat, HealthKit/Health Connect, MMKV, Encrypted Storage, i18next, Charts, Calendars.

\section*{Tech Stack}

\textbf{Front-end:} React, Angular, Next.js, Vite, Cordova, HTML5, CSS3, SASS \\
\textbf{Back-end / Infra:} Node.js, Nest.js, Java, Nginx, Webpack, Docker, Linux \\
\textbf{Testing / CI/CD:} Jest, RTL, Karma, Jenkins, GitLab/GitHub CI \\
\textbf{Databases:} Firebase, MongoDB, MySQL, MariaDB, PostgreSQL \\
\textbf{Other:} Git, Scrum, Jira, Confluence, Mapbox, TypeScript, JavaScript

\end{document}
