\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\begin{document}

\begin{minipage}[t]{0.45\textwidth} % Left column with your name and title, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Alin}}}}} % First name

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Trandafir}}}}} % Last name

	\vspace{6pt} % Vertical whitespace

	{\huge Senior Full-Stack Developer} % Career or current job title
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.27\textwidth} % Center column with the first column of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{MapMarker}{12}{Zaragoza, Spain}\\
	\icon{Phone}{12}{+34 653 751 742}\\
	\icon{At}{12}{\href{mailto:alin\_trandafir@icloud.com}{alin\_trandafir@icloud.com}}\\
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.27\textwidth} % Right column with the first column of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{Globe}{12}{\href{https://end.works}{end.works}}\\
	\icon{Github}{12}{\href{https://github.com/ender-null}{ender-null}}\\
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/alin-trandafir}{alin-trandafir}}\\
\end{minipage}

\vspace{0.5cm} % Vertical whitespace

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % Left column with the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	I'm a senior full-stack developer with \textasciitilde{}8 years of experience building scalable web and mobile applications with TypeScript. I have deep expertise in Angular, React, and React Native, working on complex SPAs, shared component systems, and production apps in enterprise and high-traffic environments.
    \\
    I value clean architecture, code quality, and maintainability. I'm comfortable leading technical direction, driving architectural decisions, and mentoring engineers, as well as owning features end to end as an individual engineer --- from design and implementation to testing and deployment. I enjoy working with multidisciplinary teams and thrive in remote and distributed environments.
    \\
    Since late 2024, I have been working independently --- building and shipping my own products while taking on client projects.
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.5\textwidth} % Right column with the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\begin{barchart}{5.5}
		\baritem{TypeScript / JavaScript}{100}
		\baritem{React}{90}
		\baritem{Angular}{90}
        \baritem{React Native}{80}
		\baritem{Node.js}{60}
        \baritem{Docker}{60}
	\end{barchart}
\end{minipage}

\cvsect{Soft Skills}
\begin{center}
Technical Leadership\slashsep Cross-functional Collaboration\slashsep Agile / Scrum\slashsep International Team Experience\slashsep Remote Work\slashsep Project Management\slashsep Problem Solving
\end{center}

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Nov 2024--Current}
		{Full-Stack Developer}
		{Freelance}
		{Built and shipped \textbf{Zierzo} and \textbf{LoveLust}, two production mobile apps live on the \textbf{App Store and Google Play}, with secure storage, real-time features, analytics, and subscription monetization --- LoveLust reaching over \textbf{13,000 monthly active users} at peak. Also deliver \textbf{websites for small local businesses} such as restaurants and shops. Own full product lifecycle: \textbf{architecture}, \textbf{CI/CD}, \textbf{testing}, and store publishing workflows. \\
        \texttt{React Native}\slashsep\texttt{Expo}\slashsep\texttt{TypeScript}\slashsep\texttt{RevenueCat}\slashsep\texttt{HealthKit/Health Connect}\slashsep\texttt{EAS}\slashsep\texttt{Firebase}\slashsep\texttt{i18next}}
	\entry
		{Oct 2022--Nov 2024}
		{Software Engineer}
		{Aimsun}
		{Owned core modules of a \textbf{SaaS platform} end to end --- authentication, accounts, subscriptions, licensing, and MFA --- within a cross-functional team. Built internal tooling for \textbf{billing}, \textbf{permissions}, and user administration. Contributed to shared auth libraries and real-time data visualization interfaces, working closely with product and design across the full feature lifecycle. \\
        \texttt{React}\slashsep\texttt{TypeScript}\slashsep\texttt{Next.js}\slashsep\texttt{i18next}\slashsep\texttt{MapBox}\slashsep\texttt{GitLab CI/CD}\slashsep\texttt{Cypress}}
	\entry
		{Dec 2021--Oct 2022}
		{Software Developer}
		{Viewnext}
		{Developed a \textbf{booking platform for EV charging stations} for a major nationwide energy company. The platform allowed users to browse available stations and sockets on an interactive map and manage all their bookings. Worked on a \textbf{shared component library}, met strict quality requirements including near-full test coverage and zero code smells. Mentored and supported junior developers with limited experience. \\
        \texttt{Angular}\slashsep\texttt{TypeScript}\slashsep\texttt{RxJS}\slashsep\texttt{Jenkins}\slashsep\texttt{GitLab CI/CD}}
    \entry
		{May 2021--Dec 2021}
		{Software Developer}
		{adidas}
		{Replaced legacy internal tooling with a modern \textbf{content editor}, cutting editorial friction significantly. Introduced \textbf{internationalization} and streamlined translation workflows across the platform. Worked in an Agile environment alongside design, content, and engineering teams. \\
        \texttt{React}\slashsep\texttt{TypeScript}\slashsep\texttt{Redux}\slashsep\texttt{i18n}}
    \entry
		{Dec 2019--May 2021}
		{Software Developer}
		{Telefónica / Eleven Paths}
		{Drove migration of a governance and risk platform to a modern \textbf{Angular} architecture. Delivered enterprise features, improved UX consistency, and maintained backend services for reporting and risk modeling. \\
        \texttt{Angular}\slashsep\texttt{TypeScript}\slashsep\texttt{RxJS}\slashsep\texttt{Java}\slashsep\texttt{i18n}}
    \entry
		{Oct 2017--Dec 2019}
		{Software Developer}
		{Ingenia Sistemas Avanzados para el Transporte}
		{Built two core products for private bus companies. The first was a \textbf{bus ticket sales platform customizable per operator}, supporting discounts, multiple payment methods, and iframe embedding for third-party websites. The second was an \textbf{internal back-office tool} for managing stations, lines, services, drivers, and vehicles, with dynamic route generation via the \textbf{Google Maps API}. Also contributed to a mobile app with real-time bus arrivals and alerts. \\
        \texttt{Angular}\slashsep\texttt{TypeScript}\slashsep\texttt{RxJS}\slashsep\texttt{Cordova}\slashsep\texttt{Stripe}\slashsep\texttt{i18n}}
    \entry
		{Mar 2017--Sep 2017}
		{Software Developer}
		{Rananegra}
		{Built dynamic websites using a modular CMS and developed custom interactive components. Created an email automation tool with subscription billing. \\
        \texttt{Symfony}\slashsep\texttt{Angular}\slashsep\texttt{TypeScript}\slashsep\texttt{Stripe}}
\end{entrylist}

\cvsect{Education}

\begin{entrylist}
	\entry
		{2014 -- 2016}
		{Multiplatform Applications Degree}
		{CPIFP Los Enlaces}
		{}

    \entry
		{2012 -- 2014}
		{Computer Systems and Networking Degree}
		{CPIFP Los Enlaces}
		{}

    \entry
		{2025}
		{Google Cloud Professional Cloud Architect}
		{Formación San Miguel}
		{}

    \entry
		{2025}
		{Oxford Test of English -- Advanced (C1)}
		{Kings Corner English School}
		{}
\end{entrylist}

\begin{minipage}[t]{0.3\textwidth} % Left column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{Spanish} --- native\\
	\textbf{English} --- C1\\
	\textbf{Romanian} --- native
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.3\textwidth} % Center column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Projects}
	\textbf{\href{https://zierzo.end.works}{Zierzo}} is a city mobility and leisure app for Zaragoza that provides \textbf{real-time public transport information}, route details, and local cinema listings, built with a strong focus on performance, scalability, and everyday usability.

    \textbf{\href{https://lovelust.end.works}{LoveLust}} is a \textbf{privacy-first wellness and intimacy tracker} designed for personal use, emphasizing data security, customization, and long-term tracking --- reaching over \textbf{13,000 monthly active users} at peak. Both projects were developed end to end with \textbf{React Native and Expo}, integrating state management, analytics, monetization, and backend services.

\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.3\textwidth} % Right column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Non-profit}
	Founded and led \textbf{Asociación Juvenil Brovrashgka}, a youth association focused on \textbf{anime and Japanese pop culture}. Organized multiple cultural events, workshops, and community activities with growing attendance. Managed \textbf{project planning}, \textbf{budgets}, \textbf{volunteers}, and event logistics. Coordinated teams, built partnerships, and delivered engaging activities for the local community.
\end{minipage}

\end{document}
