\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\begin{document}

\begin{minipage}[t]{0.45\textwidth} % Left column with your name and title, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Alin}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Trandafir}}}}} % Last name
	
	\vspace{6pt} % Vertical whitespace
	
	{\huge Full-Stack Developer} % Career or current job title
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.27\textwidth} % Center column with the first column of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome5.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Zaragoza, Spain}\\
	\icon{Phone}{12}{+34 653 751 742}\\
	\icon{At}{12}{\href{mailto:alin\_trandafir@icloud.com}{alin\_trandafir@icloud.com}}\\	
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.27\textwidth} % Right column with the first column of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome5.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://end.works}{end.works}}\\
	\icon{Github}{12}{\href{https://github.com/ender-null}{ender-null}}\\
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/alin-trandafir}{alin-trandafir}}\\
\end{minipage}

\vspace{0.5cm} % Vertical whitespace

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % Left column with the introduction text, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I'm a senior front-end developer focused on building scalable web and mobile applications with TypeScript. I have extensive experience with Angular, React, and React Native, working on complex SPAs, shared component systems, and production apps in enterprise and high-traffic environments.
    \\
    I value clean architecture, code quality, and maintainability, and I'm comfortable owning features end to end, from design and implementation to testing and deployment. I enjoy collaborating with multidisciplinary teams and taking a pragmatic, hands-on approach to leadership and mentoring.
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.5\textwidth} % Right column with the skills bar chart, change the width as needed
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\begin{barchart}{5.5} % The parameter to the barchart environment is the maximum width (in cm) of the longest bar
		\baritem{TypeScript / JavaScript}{100}
		\baritem{React}{90}
        \baritem{React Native}{80}
		\baritem{Angular}{90}
		\baritem{Next.js}{40}
		\baritem{Node.js}{60}
        \baritem{Docker}{60}
	\end{barchart}
\end{minipage}

% Output a series of bubbles showing your proficiency with environments and/or tools
\begin{center}
	\bubbles{6/TypeScript, 5/Angular, 5/React, 4/React Native, 4/Testing, 4/Cloud, 3/Backend} % Each bubble must be in the format of '<size>/<label>' and you can specify as many bubbles as will fit on the page
\end{center}

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Nov 2024--Current}
		{Full-Stack Developer}
		{Freelance}
		{Build and ship \textbf{iOS} and \textbf{Android} apps with secure storage, real-time features, analytics, and subscriptions. Also develop \textbf{websites for small local businesses} such as restaurants and shops, helping them present their products and services online. Lead \textbf{architecture}, \textbf{CI/CD}, \textbf{testing}, and full publishing workflows. Manage full product lifecycle from development to store release. \\
        \texttt{React Native}\slashsep\texttt{Expo}\slashsep\texttt{TypeScript}\slashsep\texttt{Redux Toolkit}\slashsep\texttt{RevenueCat}\slashsep\texttt{HealthKit/Health Connect}\slashsep\texttt{MMKV}\slashsep\texttt{i18next}}
	\entry
		{Oct 2022--Nov 2024}
		{Software Engineer}
		{Aimsun}
		{Built and maintained core modules for a \textbf{large SaaS platform}, including authentication, accounts, subscriptions, licensing, and MFA. Developed internal tools for \textbf{billing}, \textbf{permissions}, and user administration. Contributed to shared auth libraries and real-time data visualization interfaces. \\
        \texttt{React}\slashsep\texttt{TypeScript}\slashsep\texttt{Next.js}\slashsep\texttt{i18next}\slashsep\texttt{MapBox}\slashsep\texttt{GitLab CI/CD}}
	\entry
		{Dec 2021--Oct 2022}
		{Software Developer}
		{Viewnext}
		{Developed a \textbf{real-time monitoring dashboard} for a nationwide energy service, including route planning, maps, and booking flows. Improved API reliability, enhanced performance, and collaborated with QA to stabilize releases. \\
        \texttt{Angular}\slashsep\texttt{TypeScript}\slashsep\texttt{Jenkins}\slashsep\texttt{GitLab CI/CD}}
    \entry
		{May 2021--Dec 2021}
		{Software Developer}
		{adidas}
		{Rebuilt legacy internal tools with modern web tech, delivering an improved \textbf{content editor}. Implemented \textbf{internationalization} and optimized translation workflows. Worked with design and content teams to streamline publishing in an Agile environment. \\
        \texttt{React}\slashsep\texttt{TypeScript}\slashsep\texttt{i18n}}
    \entry
		{Dec 2019--May 2021}
		{Software Developer}
		{Telefónica / Eleven Paths}
		{Migrated a governance and risk platform to a modern \textbf{Angular} architecture. Added enterprise features, improved UX, and maintained backend services for reporting and risk modeling. \\
        \texttt{Angular}\slashsep\texttt{Java}\slashsep\texttt{i18n}}
    \entry
		{Oct 2017--Dec 2019}
		{Software Developer}
		{Ingenia Sistemas Avanzados para el Transporte}
		{Built a \textbf{responsive ticketing system} with online payments and admin tools, plus a mobile app with real-time arrivals and alerts. Collaborated with backend, design, and operations teams to improve reliability. \\
        \texttt{Angular}\slashsep\texttt{Cordova}\slashsep\texttt{i18n}}
    \entry
		{Mar 2017--Sep 2017}
		{Software Developer}
		{Ingenia Sistemas Avanzados para el Transporte}
		{Built dynamic websites using a modular CMS and developed custom interactive components. Created an email automation tool with subscription billing. \\
        \texttt{Symfony}\slashsep\texttt{Angular}\slashsep\texttt{TypeScript}\slashsep\texttt{Stripe}}
\end{entrylist}

\cvsect{Education}

\begin{entrylist}
	\entry
		{2014 -- 2016}
		{Multiplatform Applications Degree}
		{CPIFP Los Enlaces}
		{}

    \entry
		{2012 -- 2014}
		{Computer Systems and Networking Degree}
		{CPIFP Los Enlaces}
		{}

    \entry
		{2025}
		{Google Cloud Professional Cloud Architect}
		{Formación San Miguel}
		{}

    \entry
		{2025}
		{Oxford Test of English - Advanced (C1)}
		{Kings Corner English School}
		{}
\end{entrylist}

\begin{minipage}[t]{0.3\textwidth} % Left column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Spanish} - native\\
	\textbf{English} - C1\\
	\textbf{Romanian} - native
\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.3\textwidth} % Center column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Projects}
	I've developed and shipped two independent mobile applications using modern \textbf{TypeScript-based stacks}. \textbf{Zierzo} is a city mobility and leisure app for Zaragoza that provides \textbf{real-time public transport information}, route details, and local cinema listings, built with a strong focus on performance, scalability, and everyday usability.

    \textbf{LoveLust} is a \textbf{privacy-first wellness and intimacy tracker} designed for personal use, emphasizing data security, customization, and long-term tracking. Both projects were developed end to end with \textbf{React Native and Expo}, integrating state management, analytics, monetization, and backend services, and reflect my experience delivering production-ready mobile products from concept to release.

\end{minipage}
\hfill % Automatic horizontal whitespace
\begin{minipage}[t]{0.3\textwidth} % Right column width
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	Created and led a youth association focused on \textbf{anime and Japanese pop culture}. Organized multiple cultural events, workshops, and community activities with growing attendance. Managed \textbf{project planning}, \textbf{budgets}, \textbf{volunteers}, and event logistics. Coordinated teams, built partnerships, and delivered engaging activities for the local community.
\end{minipage}

\end{document}
